\documentclass{report}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
\usepackage[margin=1.2in]{geometry}
\usepackage{courier}
\usepackage{float}
\usepackage[toc,page]{appendix}
\usepackage{hyperref}
\usepackage{pdfpages}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codeblack}{rgb}{0,0,0}
\definecolor{codered}{rgb}{0.867,0,0}
\definecolor{backcolour}{rgb}{ 0.95,0.95,0.95}
\definecolor{codeorange}{rgb}{1,0.447059,0}
\definecolor{codegrey}{rgb}{0.1, 0.1, 0.1}
\definecolor{codeblue}{rgb}{0.29, 0.52, 0.56}
\lstdefinestyle{mystyle}{
    basicstyle=\ttfamily\color{codeblack},
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codered},
    keywordstyle=\color{codeorange},
    numberstyle=\color{codeblack},
    stringstyle=\color{codegreen},
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=10pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
 
\lstset{style=mystyle}

\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\ull}[1]{\underline{\underline{#1}}}
\newcommand{\triangleBrac}[1]{\textless{#1}\textgreater}
\newcommand{\un}{\textunderscore}

\begin{document}
\title{CPS3231  - Computer Graphics - Assignment Report}
\author{Daniel Cauchi}
\date{}
\maketitle

\tableofcontents

\chapter{Introduction}
This is the report for the CPS3231 - Computer Graphics assignment, where a clone of the Arkanoid game was implemented in 3D using WebGL. Object spawning, camera movement, physics, illumination and powerups were implemented and are discussed in chapters 2-6 of this report in that order. Additional features are discussed in chapter 7. A video showcase linked within a README file is also presented in order to show the game working in order. This README file will also contain any additional instructions and controls.

\input{SubFiles/ObjectSpawning}
\pagebreak
\input{SubFiles/Camera}
\pagebreak
\input{SubFiles/Physics}
\pagebreak
\input{SubFiles/Lights}
\pagebreak
\input{SubFiles/Powerups}
\pagebreak
\input{SubFiles/Extras}
\pagebreak

\chapter{Conclusion}
This concludes the report for the CPS3231 - Computer Graphics assignment. Attached to this report is a folder containing the javascript files within the 'Implementation' folder. This folder also contains a sub-folder called 'Audio' which contains all the audio used for the game. The video showcase can be found at \url{https://www.youtube.com/watch?v=AlgIYVwaaLg}. The README file contains all the controls. The report showed the features implemented and images were used to further explain the features discussed.

\pagebreak

\pagebreak
\input{SubFiles/Appendix}
\end{document}